\documentclass[fontsize=10pt]{tccv}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\begin{document}

\part{Danny Willems}

\section{Personal Profile}

Passionated about new technologies, sciences, mathematics and entrepreneurship,
I learn and practice a lot by myself besides university. I'm always ready to
learn new things.

\section{Work experience}

\begin{eventlist}

\item{July 2016 -- Novembre 2016}
	{OCaml developer. Implement OAuth2.0 and OpenID Connect server and client in
	Ocsigen-start, ocaml-jwt, binding OCaml to NodeJS with gen\_js\_api. Push
notifications in Ocsigen-start.}
	{BeSport - Ocsigen}
	@\href{https://besport.com}{BeSport}
	@\href{https://ocsigen.org}{Ocsigen} - Paris France

%\item{Novembre 2015}
	%{Developed with
	%Prestashop. Also database and server manager.}
	%{Craie à bois} @\href{http://craieabois.com}{Craie à bois}

\item{July 2015 -- Decembre 2015}
	{Supervise and develop a mobile application with Cordova. I also build an
	integration continuous system in bash.}
	 {Hybrid mobile developer} @\href{http://selfpharma.be}{Citypharma} -
	 Brussels, Belgium

\end{eventlist}

\section{Awards (Hackathons)}

\begin{yearlist}
	\item{March 2016}
		{\href{http://citizensofwallonia.be}{Citizens of Wallonia}}
		{Jury's Price - Share Your Ideas. Invited at IBM Dublin to introduce the
		project.}
	\item{October 2015}
		{\href{http://www.kissyourteacher.be/}{Kiss Your Teacher}}
		{3rd Price - ImmuneWar}
	\item{April 2015}
		{\href{http://www.be-hackathon.be/?lang=fr}{Be-hackathon}}
		{1st Price - Metro}
	\item{October 2014}
		{\href{http://sgconnectedhack.bemyapp.com/}{SGConnectedHack}}
		{3rd Price - WeCare4U}
\end{yearlist}

\section{Personal projects}

\begin{yearlist}

\item{2016}
     {\href{https://github.com/dannywillems/ocaml-cordova-plugin-list}{Binding
      OCaml to Cordova plugins}}
     {More than 40 bindings OCaml to Cordova plugins. Invited to
       \href{http://www.meetup.com/fr-FR/ocaml-paris/}{OUPS Meetup}}

%\item{2016}
     %{\href{https://github.com/dannywillems/ocaml-minilibx}{OCaml-minilibx}}
     %{Binding OCaml to minilibx, a small graphic library}

\item{2015}
     {\href{http://github.com/vim-ide/vim-ide/}{Vim-IDE}}
     {Transform the best text editor into a full IDE}

\item{2015}
     {\href{http://open-courses.org/}{Open Courses}, looking for collaborators}
     {collaborative platform containing courses on several subjects. For the
     moment, courses \href{https://github.com/open-courses}{here}}.

%\item{2015}
     %{\href{http://github.com/dannywillems/gsmath/}{GSMath}, in development}
     %{Same as GSLib but for mathematics.}

%\item{2015}
     %{\href{http://github.com/dannywillems/customizecalendars.ionic}{Customize Calendars}}
     %{Share your online calendar files, choose which events you want to go and
     %rename it as you want}

\end{yearlist}

\personal
[https://danny-willems.be]
    {Ogy, Belgium}
    {+32 (0)493 73 97 11}
    {contact@danny-willems.be}

\section{Skills}

\begin{factlist}

\item{Programming}
     {OCaml, Java, Python, C, Shell Script}

\item{Web}
	{HTML5/CSS3 (+ LESS, SASS), JavaScript + Angular JS, CMS (Wordpress,
	Prestashop)}

\item{Mobile}
	{Cordova, Ionic}
\item{Databases}
     {MySQL}

\item{OS}
     {Linux (Debian, *Ubuntu), Windows, Mac OS X}

\item{Server}
     {AWS, Debian, Kimsufi}

\item{Tools -- Others}
     {Git, LaTeX, Gulp, Grant, Yeoman, Arduino, RaspberryPi}
\end{factlist}

\section{Communication skills}

\begin{factlist}
\item{French}{Native speaker}
\item{English}{Professional knowledge}
\item{Dutch}{Elementary proficiency}
\end{factlist}

\section{Education}

\begin{yearlist}

\item[Master's degree]{2012 -- 2017}
     {Mathematics, minor in computer science and physics}
     {\href{http://umons.ac.be}{UMONS}, Mons, Belgium}

\item[Developer formation]{2015 -- 2017}
	 {Computer Science}
	 {\href{http://42.fr}{42}, Paris, France}

\end{yearlist}


\section{Personal}
\begin{factlist}
\item{Professional}{History of sciences,
	mathematics logic, web/mobile/software development, computer science theory,
Open source philosophy}
\item{Interests}{Computers, Electronics, Home automation, Technology,
	Travelling, SF Series}
\end{factlist}



\end{document}
